---
title: "Coronavirus Analysis"
author: "Navid Mohseni"
date: "5/17/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---

The coronavirus package provides a tidy format dataset of the 2019 Novel Coronavirus COVID-19 (2019-nCoV) epidemic. The raw data pulled from the Johns Hopkins University Center for Systems Science and Engineering (JHU CCSE) Coronavirus repository.

We know that COVID-19 spreads through respiratory droplets, such as through coughing, sneezing, or speaking. But, how quickly did the virus spread across the globe? And, can we see any effect from country-wide policies, like shutdowns and quarantines?

More importantly, I'll analyze my country (Iran) during this pandemic, in more details.

Let's start by taking the proper data. 
Fortunately, there is a package for coronavirus. Also, I'll load other important packages. 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
install.packages("coronavirus")
library(coronavirus)
library(tidyverse)
library(lubridate)
library(ggmap)
```

The dataset has the following fields:
* date: the date of the summary
* province: the province or state
* country: the country or region
* lat: latitude
* long: longitude
* type: type of the case (i.e., confirmed, death)
* cases: the number of daily cases

```{r}
head(coronavirus)
glimpse(coronavirus)
```

Summary of the total confirmed cases by country

```{r}
coronavirus %>% 
  filter(type == "confirmed") %>%
  group_by(country) %>%
  summarise(total_cases = sum(cases)) %>%
  arrange(-total_cases) 
```

Let's take into consideration my country: Iran in the latest day of the dataset.

```{r}
coronavirus %>% 
  filter(date == max(date)) %>%
  select(country, type, cases) %>%
  group_by(country, type) %>%
  summarise(total_cases = sum(cases)) %>%
  pivot_wider(names_from = type,
              values_from = total_cases) %>%
  arrange(-confirmed) %>% 
  filter(country == "Iran")
```
